Reproductive Allocation Calculations

### 2015-03-24 leaflifespan.Rmd
Small bug fix

# leaf lifespan data
leaf_lifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
              select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

>>>>

# leaf lifespan data
raw_leaf_lifespan <-  filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")

leaf_lifespan <- raw_leaf_lifespan %>%
              select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
